ABC Group Level Fits

### 2024-01-04 Model/dev/scratch.qmd
abc group code

  density_filename <- paste0("assets/tmp_plots/density_plots_combo_abc_", sample_size, "rmse", posterior_cutoff, ".png")
  distance_filename <- paste0("assets/tmp_plots/distance_plots_combo_abc_", sample_size, "rmse", posterior_cutoff, ".png")

>>>>

  density_filename <- paste0("assets/tmp_plots/density_plots_combo_abc_", sample_size, "_rmse_", posterior_cutoff, ".png")
  distance_filename <- paste0("assets/tmp_plots/distance_plots_combo_abc_", sample_size, "_rmse_", posterior_cutoff, ".png")
